### 2011-05-10 paper.tex
blah

@@

Suppose $L \in \Sigma\cdot C$. Then there exists a $C$ machine $M$ such that $x \in L_1$ if and only if there exists some $y$ (of length polynomial in the length of $x$) such that $M$ accepts $(x, y)$. Now, we want to construct a $\Sigma \cdot C$ machine for $\intersect(L)$; that is, given a $k$-tuple $(x_1,x_2,...,x_k)$, we want to determine if all $x_i$ are in $L$. To do this, we just guess a $k$-tuple $(y_1,y_2,...,y_k)$, and then check if $M$ accepts $(x_1, y_1)$, $(x_2, y_2)$, ..., and $(x_k, y_k)$. This is equivalent to checking that $((x_1,y_1),(x_2,y_2),...,(x_k,y_k)) \in \intersect(M)$, and by assumption, $\intersect(M)$ is in $C$ since $M$ is in $C$.

@@

Now we consider $\bp \cdot C$. By assumption, $C$ is closed under majority reductions, so by Lemma \ref{majorityimpliesamplify}, $\bp \cdot C = \strongbp \cdot C$.
\end{proof}

>>>>

\newcommand{\pr}{\text{Pr}}

@@

Suppose $L \in \Sigma\cdot C$. Then there exists a $C$ machine $M$ such that $x \in L$ if and only if there exists some $y$ (of length polynomial in the length of $x$) such that $M$ accepts $(x, y)$. Now, we want to construct a $\Sigma \cdot C$ machine for $\intersect(L)$; that is, given a $k$-tuple $(x_1,x_2,...,x_k)$, we want to determine if all $x_i$ are in $L$. To do this, we just guess a $k$-tuple $(y_1,y_2,...,y_k)$, and then check if $M$ accepts $(x_1, y_1)$, $(x_2, y_2)$, ..., and $(x_k, y_k)$. This is equivalent to checking that $((x_1,y_1),(x_2,y_2),...,(x_k,y_k)) \in \intersect(M)$, and by assumption, $\intersect(M)$ is in $C$ since $M$ is in $C$.

@@

Now we consider $\bp \cdot C$. By assumption, $C$ is closed under majority reductions, so by Lemma \ref{majorityimpliesamplify}, $\bp \cdot C = \strongbp \cdot C$. If we take any language $L \in \bp \cdot C$, we find that $L \in \strongbp \cdot C$. Therefore, there exists a $C$ machine $M$ such that $x\in L$ if and only if
\begin{center}
$\displaystyle \pr_y [M(x,y)\text{ accepts}] > $
\end{center}
\end{proof}
